Assignment 4
Submit your R notebook with your code.

```{r}
# necessary packages
library(dplyr)
library(tidyverse)
library(estimatr)
library(Rcpp)
library(stargazer)
```


Import your data into R. If you clean your data in python, you can import the csv. If you do some additional cleaning in R, be sure to show that in your R code that you hand in.

Importing my data into R
```{r}
#setting working directory
setwd("your/path/here")
#read the csv file "yelp.csv" that I scraped using Python
yelp <- read.csv("yelp.csv")

#remove scientific notation
options(scipen = 100)
```


*Run a regression with OLS. Ensure that you have more than 3 variables. (25 pts)*
```{r}
ols <- lm(Rating ~ Price.Range + log(Number.of.Reviews) + Borough, data = yelp)
summary(ols)
# log number of reviews. group locations into 5 b
```

*Run a regression with a filtered dataset (filter based on a category of your choosing within your dataset). (25 pts)*

filter dataframe by column: https://stackoverflow.com/questions/7381455/filtering-a-data-frame-by-values-in-a-column
```{r}
yelp_m <- yelp[yelp$Borough == "Manhattan",] 
ols_m <- lm(Rating ~ Price.Range + log(Number.of.Reviews), data = yelp_m)
summary(ols_m)
```

*Run your preferred regression using your dataset (different from regression 3). (25 pts)*

```{r}
ols_p <- lm(log(Number.of.Reviews) ~ Price.Range + Rating + Borough, data = yelp)
summary(ols_p)
```
```{r}
stargazer(ols, ols_p, ols_m, type="html", 
          title = "Cross-Sectional Data Results",
 dep.var.labels=c("Rating", "log of Number of Reviews","Rating in Manhattan"),
 covariate.labels=c("Price Range", "log of Number of Reviews", "Rating"), out="Regression.html")
```



*Write a few sentences about your preferred regression. Interpret the coefficients that are most important to you and discuss the statistical significance. (25 pts)*

Regression 1 shows that holding the number of reviews and location of the restaurant constant, there is no significant effect of the change in price on the rating. 

In addition, for each 100% additional reviews, a restaurant’s rating will fall by 0.09 stars, holding price and location constant. 

The omitted variable here is Bronx. Therefore, the coefficients on the location variables are their ratings compared with Bronx. Holding the number of reviews and price constant, restaurants in Queens have the highest average ratings, and restaurants in Bronx have the lowest ratings.

Regression 2 shows that an 1-star increase in rating is associated with a 130% decline in the predicted number of reviews, holding price range and location constant.

Regression 3 shows that in Manhattan, for each 100% additional reviews, a restaurant’s rating will fall by 0.08 stars.

In conclusion, there seems to be little impact of price on the number of reviews a restaurant receives. The algorithm that Yelp uses to draw the best 240 restaurants in each borough is uncertain, so that the collection of my sample is not randomized and Yelp might omit valuable observations that can help me improve my regressions. 

In addition, the number of reviews may not be a good indicator of the popularity of the restaurants, given that some restaurants may provide discounts or other way to incentivize customers to leave reviews.

